Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-05-05 tex/paper1/paper1.tex
edits to the paper

\subsection{Nature of the power law power spectrum}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
red-noise like power spectrum.  It is present in both wavebands
studied and in all the regions, and so parsimony suggests that the
mechanism of its creation is both similar and ubiquitous in all parts
of the solar atmosphere.  We hypothesize that the \PL\ \PS\ is due to
the sum of a distribution of a large number of energy deposition
events having different energies. \cite{} describes how a
\PL\ \PS\ may obtained from such a distribution, and that argument
outlined below.

Each energy deposition event is modeled as an exponentially decaying
function of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and energy $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(f) = \frac{E}{1 + (2\pi f T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{T}(f) = \sum_{T}N(T)P_{T}(f)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
energy $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the energy in each event depends on its time scale $T$ such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown \cite{} that the observed power spectrum can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P(f) \propto f^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}

This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar events.  The detailed
application of this model of the observed background \PL\ power
spectra will depend strongly on three factors that influence the
observation.  Firstly, the distribution of events along the line of
sight and their temporal dependence (expressed through the parameters
$\alpha_{E}$ and $\gamma$ in Equation \ref{eqn:energydistrib}) have
strong effects on the observed \Fps.  Secondly, the physics of the
radiation emitted as a function of the energy deposited in each event
and the existing plasma properties must be consistently modeled.
Finally, the properties of the observing instrument, in this case the
AIA filters, will also influence the observed \Fps.  These three
factors must be modeled in order to confirm or deny the hypothesis
that ubiquitous energy deposition events are the root cause of the
observed Fourier power spectra.

@@

>>>>

\subsection{Nature of the power law power spectrum}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
red-noise like power spectrum.  It is present in both wavebands
studied and in all the regions, and so parsimony suggests that the
mechanism of its creation is both similar and ubiquitous in all parts
of the solar atmosphere.  We hypothesize that the \PL\ \PS\ is due to
the sum of a distribution of a large number of energy deposition
events having different energies. \cite{2011soca.book.....A} describes
how a \PL\ \PS\ may obtained from such a distribution, and that
argument outlined below.

Each energy deposition event is modeled as an exponentially decaying
function of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and energy $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{T}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
energy $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the energy in each event depends on its time scale $T$ such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown \cite{} that the observed power spectrum can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}

This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar events.  The detailed
application of this model of the observed background \PL\ power
spectra will depend strongly on three factors that influence the
observation.  Firstly, the distribution of events along the line of
sight and their temporal dependence (expressed through the parameters
$\alpha_{E}$ and $\gamma$ in Equation \ref{eqn:energydistrib}) have
strong effects on the observed \Fps.  Secondly, the energy radiated as
a function of the energy deposited in each event and the existing
plasma properties must be consistently modeled.  This is required to
understand how much radiation at each wavelength is emitted from the
plasma.  Finally, the AIA instrument filters the emitted radiation,
and this too must be modeled in order to understand the observed \Fps.
These three features must be modeled in order to test the hypothesis
that ubiquitous energy deposition events are the root cause of the
observed power-law like behavior of the Fourier power spectra.

There has been a considerable amount of work in modeling the
AIA-detected plasma response.  \cite{}

@@

Comparing the \Fps\ of the simulated observations to the \Fps\ of the
data will bring new constraints on the simulations that will hopefully
improve our understanding of the temporal behavior of the solar corona.
